Air Quality and CMS Data

### 2021-02-01 code/data-analysis/config-file-generator.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r ses adj. model for factors - urban}
dataname <- "ndi-fac-urban.csv"
expo <- fac
subg <- "urb"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-urban', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - rural}
dataname <- "ndi-fac-rural.csv"
expo <- fac
subg <- "rur"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-rural', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

@@

```{r ses adj. model for factors - west}
dataname <- "ndi-fac-west.csv"
expo <- fac
subg <- "rW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-west', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - midwest}
dataname <- "ndi-fac-midwest.csv"
expo <- fac
subg <- "rMW"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-midwest', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - south}
dataname <- "ndi-fac-south.csv"
expo <- fac
subg <- "rS"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-south', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

```{r ses adj. model for factors - northeast}
dataname <- "ndi-fac-northeast.csv"
expo <- fac
subg <- "rNE"

for (i in seq(1,length(expo),1)){
  filenames <- c( tempfile())
  for( f in  filenames ){
    cat(config.em.2, file=f)
    x <- readLines(f)
    y <- gsub("dataset", dataname, x)
    z <- gsub("exposure", expo[i], y)
    s <- gsub("subg", subg, z)
    for (j in seq(1,length(cuz.sub),1)){
      w <- gsub("outcome", cuz.sub[j], s)
      cat(w, file=f, sep="\n")
      k=j+length(cuz.sub)*(i-1)
      writeLines(w, here('config-files','fac-northeast', paste(k,'.txt', sep = "")))
    }
  }
  file.remove(f)
  }
```

### 2021-02-01 code/data-analysis/factor-analysis.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

@@

```{r Removing EC from factor analysis}
fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings.ex.ec <- rbind(fit$loadings)
save(factor.loadings.ex.ec, file = here('output','table','factor-loadings-ex-ec.RDa'))
# Soil Metals Traffic Biomass Coal Salt Oil Steel

>>>>

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r Removing EC from factor analysis}
fit <- factanal(dt.pmc.daily %>% select(AS:ZN, OC), 8, rotation="varimax")
factor.loadings.ex.ec <- rbind(fit$loadings)
save(factor.loadings.ex.ec, file = here('output','table','factor-loadings-ex-ec.RDa'))
# Soil Metals Traffic Biomass Coal Salt Oil Steel
write.csv(factor.loadings.ex.ec,
          file = here('output','table', 'factor-loadings.csv'))

### 2021-02-01 code/data-processors/air-data-processor.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

dt.pmc.site.ndi %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
# urban 72
# suburban 69
# rural 174
# ...   2
```

@@

>>>>

dt.pmc.site.ndi %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
# urban 72
# suburban 69
# rural 176

dt.pmc.site.ndi %>% 
  group_by(Region.IV, Location.Setting) %>% 
  summarise(n = n())
#1	102			
#2	68			
#3	93			
#4	54

dt.pmc.site.ndi.bz6 <- read.csv(here('data', 'processed', 'site_pmc_ndi_bz6.csv')) %>% 
  rename(Site.ID = Site_ID) %>% 
  left_join(dt.aqs.sites)

dt.pmc.site.ndi.bz6 %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
```

@@

```{r}
load(here('data','processed', 'pmc-daily.RDa'))
load(here('data','processed','pmc-site-ndi.RDa'))

dt.pmc <- dt.pmc.site.ndi %>% 
  mutate(Loc.Set = ifelse(Location.Setting == "RURAL", "Rural", "Urban"),
         Region = ifelse(Region.IV == 1, "W",
                         ifelse(Region.IV == 2, "MW",
                                ifelse(Region.IV == 3, "S", "NE")))) %>% 
    select(Site.ID, Region, Loc.Set) %>% 
  merge(dt.pmc.daily) %>% 
  pivot_longer(AS:PM,
               names_to = "Parameter",
               values_to = "Value")

table.region <- dt.pmc %>% 
  group_by(Parameter, Region) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000)))

table.urban <- dt.pmc %>% 
  group_by(Parameter, Loc.Set) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  rename(Region = Loc.Set)

table <- dt.pmc %>% 
  group_by(Parameter) %>% 
  summarise(Mean = sprintf("%0.2f", mean(Value*1000)),
            STD = sprintf("%0.2f", sd(Value*1000))) %>% 
  mutate(Region = "US") %>% 
  as.data.frame() %>% 
  add_row(table.region) %>% 
  add_row(table.urban) %>% 
  pivot_wider(names_from = c(Region),
              values_from = c(Mean, STD))

write.csv(table,
          file = here('output','table', 'pmc-daily-summary.csv'),
          row.names = F)

```

### 2021-02-01 code/data-processors/cms-data-processor.Rmd
CMS, config files, output cleaning for factor em analysis - PMC data summary - Plot functions - plot making

---
title: "Air Quality and CMS Data"
author: "Fatemeh Kazemi"
date: "1/18/2021"
output: html_document
---

@@

### Note:
  1. In data merged with CMS, bufferzone is 12-mile unless specified
  2. Exposure window is one year unless specified

@@

### LE 75
dt.ndi.fac.ageLE75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aLE75 = ifelse(age == "LE", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### M 75
dt.ndi.fac.ageM75 <- dt.age %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aM75 = ifelse(age == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.sex <- dt.master.ndi.pmc %>% 
    select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses)

@@

### Race Asian
dt.raceA <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "A", "O", "A")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

### Race Black
dt.raceB <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

### Race Hispanic
dt.raceH <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

### Race White
dt.raceW <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceA <- dt.raceA %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rA = ifelse(race == "A", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race Black
dt.raceB <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceB <- dt.raceB %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rB = ifelse(race == "B", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race Hispanic
dt.raceH <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceH <- dt.raceH %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rH = ifelse(race == "H", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race White
dt.raceW <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceW <- dt.raceW %>% 
  inner_join(dt.fac.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rW = ifelse(race == "W", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

@@

@@

```{r PMC BRFSS}
dt.pmc <- dt.pmc.1yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc.brfss, 
          file = here('data', 'processed', 'ndi-pmc-brfss.csv'),
          row.names = F)
```

>>>>

---
title: "Air Quality and CMS Data"
author: "Fatemeh Kazemi"
date: "1/18/2021"
output: html_document
---
#####To do for fututre/ not urgent in all
##### Fix Factor with and wothout EC names####

@@

### Note:
  1. In data merged with CMS, bufferzone is 12-mile unless specified
  2. Exposure window is one year unless specified
  4. In mail analysis (factors and risudal of factors) dt.fac.1yr is factor
    analysis with EC and datasets are saved as fac.
  3. In all Effect modification analysis, the fac.ex.ec is saved as fac

@@

### LE 75
dt.ndi.fac.ageLE75 <- dt.age %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aLE75 = ifelse(age == "LE", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### M 75
dt.ndi.fac.ageM75 <- dt.age %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(aM75 = ifelse(age == "M", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

dt.sex <- dt.master.ndi.pmc %>% 
    select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>%  
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses)

@@

### Race Asian
dt.raceA <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "A", "O", "A")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

### Race Black
dt.raceB <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

### Race Hispanic
dt.raceH <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

### Race White
dt.raceW <- dt.master.ndi.pmc.race %>%
  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceA <- dt.raceA %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rA = ifelse(race == "A", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race Black
dt.raceB <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "B", "O", "B")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceB <- dt.raceB %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rB = ifelse(race == "B", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race Hispanic
dt.raceH <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "H", "O", "H")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceH <- dt.raceH %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rH = ifelse(race == "H", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

### Race White
dt.raceW <- dt.master.ndi.fac.race %>%
  mutate(race = ifelse(!race == "W", "O", "W")) %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards)

@@

dt.ndi.fac.raceW <- dt.raceW %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  mutate(rW = ifelse(race == "W", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race)

@@

```{r Factor urbanicity}
#fatemeh
fac <- c("Factor1","Factor2","Factor3","Factor4",
         "Factor5","Factor6","Factor7","Factor8")

### Urban and Suburban
dt.ndi.fac.urban <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(urb = ifelse(!Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

for (cmp in fac){
    dt.ndi.fac.urban[ ,paste0("urb_",cmp)] <- 
      dt.ndi.fac.urban[ ,cmp] * dt.ndi.fac.urban$urb
}

dt.ndi.fac.urban <- dt.ndi.fac.urban %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, urb, everything())

write.csv(dt.ndi.fac.urban, 
          file = here('data', 'processed', 'ndi-fac-urban.csv'),
          row.names = F)

### Rural
dt.ndi.fac.rural <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rur = ifelse(Location.Setting == "RURAL", 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Location.Setting)

for (cmp in fac){
    dt.ndi.fac.rural[ ,paste0("rur_",cmp)] <- 
      dt.ndi.fac.rural[ ,cmp] * dt.ndi.fac.rural$rur
}

dt.ndi.fac.rural <- dt.ndi.fac.rural %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rur, everything())

write.csv(dt.ndi.fac.rural, 
          file = here('data', 'processed', 'ndi-fac-rural.csv'),
          row.names = F)
```

@@

```{r Factor Region}
fac <- c("Factor1","Factor2","Factor3","Factor4",
         "Factor5","Factor6","Factor7","Factor8")

### West = 1
dt.ndi.fac.west <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rW = ifelse(Region.IV == 1, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

for (cmp in fac){
    dt.ndi.fac.west[ ,paste0("rW_",cmp)] <- 
      dt.ndi.fac.west[ ,cmp] * dt.ndi.fac.west$rW
}

dt.ndi.fac.west <- dt.ndi.fac.west %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rW, everything())

write.csv(dt.ndi.fac.west, 
          file = here('data', 'processed', 'ndi-fac-west.csv'),
          row.names = F)

### Midwest = 2
dt.ndi.fac.midwest <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rMW = ifelse(Region.IV == 2, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

for (cmp in fac){
    dt.ndi.fac.midwest[ ,paste0("rMW_",cmp)] <- 
      dt.ndi.fac.midwest[ ,cmp] * dt.ndi.fac.midwest$rMW
}

dt.ndi.fac.midwest <- dt.ndi.fac.midwest %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rMW, everything())

write.csv(dt.ndi.fac.midwest, 
          file = here('data', 'processed', 'ndi-fac-midwest.csv'),
          row.names = F)

### South = 3
dt.ndi.fac.south <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rS = ifelse(Region.IV == 3, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

for (cmp in fac){
    dt.ndi.fac.south[ ,paste0("rS_",cmp)] <- 
      dt.ndi.fac.south[ ,cmp] * dt.ndi.fac.south$rS
}

dt.ndi.fac.south <- dt.ndi.fac.south %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rS, everything())

write.csv(dt.ndi.fac.south, 
          file = here('data', 'processed', 'ndi-fac-south.csv'),
          row.names = F)

### Northeast = 4
dt.ndi.fac.northeast <- dt.master.ndi.pmc %>% 
  select(Site.ID:no_death_lungc,
         -no_death_nacc, -no_death_acc,
         -no_death_uri, -no_death_ards) %>% 
  inner_join(dt.fac.ex.ec.1yr) %>% 
  inner_join(dt.ses) %>% 
  inner_join(dt.site) %>% 
  mutate(rNE = ifelse(Region.IV == 4, 0,1),
         StrID = paste(age, sex, race)) %>% 
  select(-age, -sex, -race, -Region.IV)

for (cmp in fac){
    dt.ndi.fac.northeast[ ,paste0("rNE_",cmp)] <- 
      dt.ndi.fac.northeast[ ,cmp] * dt.ndi.fac.northeast$rNE
}

dt.ndi.fac.northeast <- dt.ndi.fac.northeast %>% 
  rename(SiteID = Site.ID) %>% 
  select(SiteID, Year, Month, StrID, rNE, everything())

write.csv(dt.ndi.fac.northeast, 
          file = here('data', 'processed', 'ndi-fac-northeast.csv'),
          row.names = F)
```

@@

```{r PMC BRFSS}
cmp.sub <- c("SE", "CA", "CL", "NA", "NI", "NO3", "OC", 
             "PB", "PM", "SI", "SO4", "V", "ZN")

dt.pmc <- dt.pmc.1yr %>% 
  rename_at(cmp.sub, ~paste("Yr", .x, sep = "_"))

@@

write.csv(dt.ndi.pmc.brfss, 
          file = here('data', 'processed', 'ndi-pmc-brfss.csv'),
          row.names = F)

pmc.brfs.count <- dt.ndi.pmc.brfss %>% 
  distinct(SiteID, Year, Month) %>% 
  rename(Site_ID = SiteID)

write.csv(pmc.brfs.count, 
          file = here('data', 'processed', 'pmc-brfss-count.csv'),
          row.names = F)

dt.pmc.site.ndi.brfs <- dt.ndi.pmc.brfss %>% 
  rename(Site.ID = SiteID) %>% 
  distinct(Site.ID) %>% 
  merge(dt.pmc.site.ndi)

dt.pmc.site.ndi.brfs %>% 
  group_by(Location.Setting) %>% 
  summarise(n = n())
#RURAL	37			
#SUBURBAN	42			
#URBAN	56	> 98
```
